Liptschiz

### 2024-02-14 lipschitz/Lipitschz.tex
debug

\title{I Compensate, therefore I Am \\ (accurate for DNN verification)}
\date{}

@@

	\begin{abstract}
		Deep Neural Networks (DNNs) verification is now a mature research field, with many methodologies and tools to verify formally that they are correct, with an annual competition to compare them, etc. Formally, the question is, given a DNN and a property to check, does the property hold over a set of inputs of the DNN. This allows e.g. to check local robustness around an input $\vx$, by checking that the i-th output neuron has the largest weight among all output neurons uniformly over a neighbourhood around $\vx$. In the most recent years, the focus has been on combining several of these efficient techniques (branch and bound, multi neuron encoding, MILP encoding, ...) to optimize speed/accuracy trade-offs. While some relatively large DNNs (tens of thousands of neurons) can be checked very efficiently with modern verifiers, some DNNs are still challenging to address with efficient algorithms, even small ReLU DNNs with hundreds of neurons, showing the need for new methodologies.

		In this paper, we analyse efficient algorithms to verify ReLU DNNs, based on abstractions (DeepPoly, Linear Programming, PRIMA, different version of Crown), and uncover the main reason for the loss of accuracy, namely {\em compensations}. Intuitively, a compensation happens when there are 2 paths between the same pair of neurons, one path with positive and one path with negative (product of) weights, which therefore (partly) compensate each other. It is however hard to compute exactly by how much is the compensation due to the ReLU activation functions. Based on this finding, we propose a novel methodology to obtain interesting trade-offs in terms of speed/accuracy, using many queries with few 'open' ReLU nodes (for which both linear modes are considered), rather than the usual few queries with potentially many 'open' ReLU nodes. These promising results open up many different applications of the concept of compensating paths in the field of verification of DNNs.  
	\end{abstract}

@@

	\input{introduction}

	\input{relatedwork}

@@

\input{comppaths}

\input{experiments}

@@

In this paper, we introduced the notion of {\em compensating pairs of paths}, with rationale why such a phenomenon creates inaccuracies hard to handle when verifying DNNs. We proved that this phenomenon is actually explaining entirely the inaccuracies, as in their absence, even the simplest Box abstraction (interval arithmetic) suffices to verify accurately DNNs. We verified experimentally that DNNs learnt in a natural way, harder to verify than robustly trained DNNs, exhibit paths with larger compensating strength.

Based on this idea of compensating pairs of paths, we proposed abstraction $\MILP_{Z}$ considering a subset $Z$ of the set of unstable ReLU nodes, that we proved to be fully accurate if {\em all} the compensating paths are covered by $Z$. Our empirical studies revealed that selecting $Z$ to cover only {\em a few} paths with the most significant compensation yields highly accurate results. Additionally, we observed that the runtime can be advantageous in certain scenarios, though not universally. This underscores the potential of compensating strength as an innovative and promising avenue for enhancing DNN verification.
 We finally proposed several ways to use the compensating strength to optimize current tools in different directions, and leave that as future work.

@@

\appendix

\input{proofs}

>>>>

\title{Liptschiz}
\date{}

@@

	\begin{abstract}

		Local robustness is bad. We study a more global notion, lipsitcz constant.

	\end{abstract}

@@

	TO DO.

@@

@@

@@
